---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# dataViewer

#### Daniel Padfield, dp323@exeter.ac.uk

An RStudio Addin for data visualisation, exploratory analysis and identifying outliers.

## Issues and suggestions

Please report any issues or suggestions in the issues tab [here](https://github.com/padpadpadpad/dataViewer/issues)

Mac : [![Build Status](https://travis-ci.org/padpadpadpad/dataViewer.svg?branch=master)](https://travis-ci.org/padpadpadpad/dataViewer)

## Overview and installation

dataViewer is a package containing an RStudio addin that allows for visualisation of large datasets, exploratory analyses and easier identification of points of interest within the dataset.

```{r}
devtools::install_github('padpadpadpad/dataViewer')

library(dataViewer)
```

## Using dataViewer

dataViewer can be called within a script to explore datasets. I will show a few uses of the dataset by first ysing the `msleep` dataset within `ggplot2`. I had no idea this existed until just now but seems like a cool dataset describing the sleeping characteristics of mammals.

Firstly we can see all the data on a single plot split by a colour. 

```{r}
# load package

# load in dataset
data("msleep")

# run dataViewer
dataViewer(ChickWeight, x = 'Time', y = 'weight', id_col = 'Diet', lm_fit = T)

```
